%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{green}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{Luc}
\familyname{Leonard}
%\address{20 tr}{(omitted for web)}    % optional, remove the line if not wanted
\mobile{07 61 43 68 70}                    % optional, remove the line if not wanted
\email{luc.leonard2@gmail.com}                      % optional, remove the line if not wanted
%\homepage{http://markliu.me}                % optional, remove the line if not wanted
%\extrainfo{\url{http://markliu.me}} % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{2009--2014}{Expert en technologie de l'information}{Epitech}{}{}{}
\cventry{2012--2013}{MSC Advanced Computer Science}{University of Kent in Canterbury}{Canterbury}{}{}

\section{Experience}

\cventry{mars 2015--courant}{Developpeur}{Numvision}{La Ciotat}{}{
Developpement de solutions de synchronisation et d'envoi de fichiers.
Developpement d'application web java (J2EE, Primefaces, Spring Boot).
Developpement d'application mobiles (Apache Cordova).
Developpement d'add-in Outlook.
Developpement de plugins Thunderbird.
}

\cventry{2013--2014}{Developpeur}{CMA-CGM}{Marseille}{}{
Developpement d'applications web SPA en javascript (ext-JS)
}

\cventry{mai 2012--aout 2012}{Developpeur}{Numvision}{La Ciotat}{}{
Developpement d'un logiciel et d'une application web de synchronisation de fichiers
}

\cventry{2011--2012}{Assistant Epitech region}{EPITECH}{Marseille}{}{
Organisation de TDs et de soutenances. Cours. Gestion de la logistique des journees portes ouvertes.
}

\cventry{juillet 2011--aout 2011}{Developpeur}{Gemalto}{La Ciotat}{}{
Developpement d'un prototype de solution de partage de fichiers chiffres a l'aide d'une carte NFC
}


\section{Competences}
\subsection{Maitrise}
\cvline{languages}{C, C++, JavaScript, Java}
\cvline{technologies}{Spring, Spring Security, Spring Boot, Apache Cordova, J2EE, Linux, FreeBSD, Nginx, SVN, git, bash}
\subsection{Connait}
\cvline{languages}{PHP, C#, OCaml, Python, Ruby, shell}
\cvline{technologies}{Apache, Jenkins, Maven, ExtJS, Django}
\section{Autre}
\cventry{}{}{}{}{}{
Backpacking, production musicale
}

\end{document}
